---
title: "Notes"
author: William Argiroff
output: html_document
date: "2025-01-15"
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Setup  

Load `devtools`.  

```{r devtools, eval = FALSE}
library(devtools)
```

Create directory to hold the package (needs to be its own git repository, not part of another project).  

```{r create_directory, eval = FALSE}
dir.create("~/Documents/github_repos/regexcite")
```

Create the package.  

```{r create_package, eval = FALSE}
create_package("~/Documents/github_repos/regexcite")
```

Commit changes.  

```{r git, eval = FALSE}
use_git()
```

Add `.Rprofile` file to automatically load `devtools` when the session starts. Add a line with `library(devtools)`. Commit those changes using the `git` window.    

Then create a `.R` file under the `R\` directory to hold the script.  

```{r create_r_file_for_strsplit1, eval = FALSE}
use_r("strsplit1")
```

Add function to `strsplit1.R`.  

```{r add_function, eval = FALSE}
strsplit1 <- function(x, split){

  strsplit(x, split = ",")[[1]]

}
```

Load everything in `R/` directory into session.  

```{r load, eval = FALSE}
load_all()
```

