---
title: "Notes"
author: William Argiroff
output: html_document
date: "2025-01-15"
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Resources  

Pat Schloss [Code Club Episode](https://www.youtube.com/watch?v=XjolVT16YNw&t=220s)  

[R Packages](https://r-pkgs.org), Chs. 1 and 2  

# Setup  

Load `devtools`.  

```{r devtools, eval = FALSE}
library(devtools)
```

Create directory to hold the package (needs to be its own git repository, not part of another project).  

```{r create_directory, eval = FALSE}
dir.create("~/Documents/github_repos/regexcite")
```

Create the package.  

```{r create_package, eval = FALSE}
create_package("~/Documents/github_repos/regexcite")
```

Commit changes.  

```{r git, eval = FALSE}
use_git()
```

Add `.Rprofile` file to automatically load `devtools` when the session starts. Add a line with `library(devtools)`. Commit those changes using the `git` window.    

Then create a `.R` file under the `R\` directory to hold the script.  

```{r create_r_file_for_strsplit1, eval = FALSE}
use_r("strsplit1")
```

Add function to `strsplit1.R`.  

```{r add_function, eval = FALSE}
strsplit1 <- function(x, split){

  strsplit(x, split = ",")[[1]]

}
```

Load everything in `R/` directory into session.  

```{r load, eval = FALSE}
load_all()
```

Check progress.  

```{r check, eval = FALSE}
check()
```

Look at DESCRIPTION file. Fill in missing information. In console, add license using this command (which will update the DESCRIPTION and LICENSE files accordingly).  

```{r license, eval = FALSE}
use_mit_license()
```

Add documentation using `roxygen2`. Go to `strsplit.R` file and then Code > Insert roxygen skeleton. Fill in the missing values. Then document.   

```{r document, eval = FALSE}
document()
```

Preview what the help documentation will look like.  

```{r preview_help, eval = FALSE}
?strsplit1
```

Several files change, including NAMESPACE. `export(strsplit1)` is added due to @export line in `roxygen2` comment. Run another check excluding vignettes so the `inst/doc/` directory is not deleted.  

```{r check_again, eval = FALSE}
check(".", vignettes = FALSE)
```
 
Then install and load. 

```{r install, eval = FALSE}
install()
library(regexcite)
```

Automate testing of functions with `testthat`. Automating tests allows you to catch issues that arise when changes in one part of the package break other parts. First, initialize with `testthat`.  

```{r initialize_testing, eval = FALSE}
use_testthat()
```

This creates a `test/` directory that contains a standard `testthat.R` script (don't touch this) and a `man/` directory with documentation for each function. There is also a `tests/testthat/` directory, which will contain R scripts for tests.  

To start, initiate a test of the function.  

```{r start_strsplit1_test, eval = FALSE}
use_test("strsplit1")
```

This creates `tests/testthat/test-strsplit1.R`. Go this script and then go to Build > Test. It then runs the test. Can also run the following:  

```{r test, eval = FALSE}
test()
```

It says everything is good, but that's because it was a default test. We need to write our own for the function.    

```{updated_test, eval = FALSE}
test_that("strsplit1() splits a string", {
  expect_equal(strsplit1("a,b,c", split = ","), c("a", "b", "c"))
})
```


